### 2013-10-19 chi2014/introduction.tex
10 pages

We asked individuals to brainstorm ways to use an MP3 player whose batteries were dead. We varied the number of ideas requested (5, 10, 20, 50, 75, 100, or unlimited), paying a fixed amount per idea (3.5 cents). Across all conditions, 154 workers submitted responses to 170 HITs (Human Intelligence Tasks), yielding 3292 ideas. From these ideas, we present a series of models characterizing features of crowd brainstorming: the rate of novel idea production, the rate at which novel {\em categories\/} of ideas are produced, qualities of the ideas (for example, whether they are common or not), and characteristics of the brainstorming process itself.

Our primary findings and contributions are as follows:
\begin{itemize}
\item The rates at which novel ideas and categories of ideas are produced follow an exponential model, decreasing exponentially over time.
%\item The rates for generating novel ideas changes with the number of responses requested per individual, even if the overall number of responses is held constant. In general, a higher rate of novel idea generation is achieved by asking fewer participants for more responses each. This result corresponds to previous finding that making participants to extend more effort generating ideas--in this case by requiring them to generate a lot of ideas--will lead to an increasing proportion of good ideas\cite{parnes_effects_1961}.
%[TODO: There is likely past work that has a similar finding; we should relate this finding to it. Taylor Berry Block as related? Diehl as related?][Pao's note: can't find more directly related stuff mainly because most of the previous lit focus on time limit task rather than number of ideas. This is actually a good argument for the paper since time limit might not work in this marketplace.]
\item People are likely to come up with the same overall set of ideas early in their brainstorming process, but then diverge from this set of common ideas as they generate more ideas. Given our results, we find there is little value in requesting fewer than 20 ideas from workers, since these early ideas are among the most common.
\item Individuals' patterns of idea generation mimic those identified by Nijstad and Stroebe's SIAM (search for ideas in associative memory) model \cite{nijstad_how_2006}: Workers produce a set of ideas from working memory, then switch strategies to generate ideas that are permutations of other ideas, a process we dub {\em riffing\/}. %We also replicate Nijstad and Stroebe's findings with respect to the time it takes to generate a new idea \cite{nijstad_how_2006}.
\item we identify and describe a set of strategies employed by crowd workers that result in distinct kinds of produced ideas
\end{itemize}

>>>>

We asked individuals to brainstorm ways (5, 10, 20, 50, 75, 100, or as many as possible) to use an MP3 player whose batteries were dead, paying a fixed amount per idea (3.5 cents). 154 workers submitted responses to 170 HITs (Human Intelligence Tasks), yielding 3292 ideas. We create a series of models characterizing features of crowd brainstorming: the rate of novel idea production, the rate at which novel {\em categories\/} of ideas are produced, qualities of the ideas (for example, whether they are common or not), and characteristics of the brainstorming process itself.

Our primary findings and contributions are as follows:
\begin{itemize}
\item The rates at which novel ideas and categories of ideas are produced follow an exponential model, decreasing exponentially over time.
%\item The rates for generating novel ideas changes with the number of responses requested per individual, even if the overall number of responses is held constant. In general, a higher rate of novel idea generation is achieved by asking fewer participants for more responses each. This result corresponds to previous finding that making participants to extend more effort generating ideas--in this case by requiring them to generate a lot of ideas--will lead to an increasing proportion of good ideas\cite{parnes_effects_1961}.
%[TODO: There is likely past work that has a similar finding; we should relate this finding to it. Taylor Berry Block as related? Diehl as related?][Pao's note: can't find more directly related stuff mainly because most of the previous lit focus on time limit task rather than number of ideas. This is actually a good argument for the paper since time limit might not work in this marketplace.]
\item People are likely to come up with the same overall set of ideas early in their brainstorming process, but then diverge from this set of common ideas as they generate more ideas. We find there is little value in requesting fewer than 20 ideas from workers.
\item Individuals' patterns of idea generation mimic those identified by Nijstad and Stroebe's SIAM (search for ideas in associative memory) model \cite{nijstad_how_2006}: Workers produce a set of ideas from working memory, then switch strategies to generate ideas that are permutations of other ideas, a process we dub {\em riffing\/}. %We also replicate Nijstad and Stroebe's findings with respect to the time it takes to generate a new idea \cite{nijstad_how_2006}.
\item we describe a set of strategies employed by crowd workers that result in distinct kinds of produced ideas
\end{itemize}

### 2013-10-19 chi2014/method.tex
10 pages

\subsection{Recruitment and Remuneration}
To study brainstorming in a crowd environment, we published brainstorming HITs (human intelligence tasks) on Amazon's Mechanical Turk. We restricted our worker pool to residents of the United States to increase the chances of English language comprehension and a shared cultural background. No other screening was performed on workers.

HITs were placed on the marketplace asking for 5, 10, 20, 50, 75, 100, or an unlimited number of ideas for a brainstorming problem. We paid a fixed amount per HIT, computed at a rate of approximately 3.5 cents per idea requested, yielding reward amounts of 18 cents (5), 35 cents (10), 70 cents (20), \$1.75 (50), \$2.65 (75), and \$3.50 (100). For the unlimited condition, we offered \$1.75, pricing it the same as the 50 ideas condition. HITs were advertised with the number of responses requested. Workers had 18 hours to submit the HIT once accepted.

\subsection{Brainstorming Question: Uses for an Old MP3 Player}
In conducting this research, we tested several brainstorming questions, including classic brainstorming questions from prior work (e.g., ``provide alternative uses for a mop''); a request to brainstorm factors that influence weight gain and weight loss; and more goal-oriented questions, such as one requesting people to brainstorm ways to raise funds for a charity. Ultimately, we found the goal-oriented brainstorming questions to be the most compelling since they reflect what we believe would be real-world uses of brainstorming on Mechanical Turk.

The final brainstorming question we chose for this research is the following:
\begin{quote}
{\em Many people have old MP3 players or MP3 players that they no longer use. Please brainstorm N uses for old MP3 players/MP3 players. Assume that the devices' batteries no longer work, though they can be powered via external power sources. Also be aware that devices may {\em not \/} have displays. Be as specific as possible in your descriptions.\/}
\end{quote}

@@

We chose to focus on this problem because a) we expected workers to be familiar with problem area (old MP3 players), b) it represents a real-world problem (what to do with old electronics that are still partially functional) for which innovative solutions are welcome, and c) we anticipated there to be a wide range of creative solutions possible. All data presented in this paper refer only to responses received to this particular question.

@@

The introduction listed Osborne's four rules of brainstorming \cite{osborn_applied_1957}, adapted to this context:

\begin{enumerate}
\item There are no bad ideas. Don't criticise your choices.
\item Wild ideas and building off of old ideas are okay.
\item Quantity of ideas is prioritized.
\item Combinations of ideas count as new ideas.
\end{enumerate}

In addition to the visible text input fields, HITs were instrumented to collect the time of the first activation and last de-activation of each form element.

@@

154 workers submitted 170 HITs, for a total of 3292 responses. As we received data in the unlimited condition, it became obvious that this was a poor strategy to employ -- the number of responses received was less than 15 in all cases. Accordingly, we remove that data from our analysis.

If a worker completed multiple HITs, there is the possibility that their responses and idea generation processes evolved over time. Accordingly, we retain only the first HIT submitted by each worker.

After removing these data, we are left with 146 distinct participants for a total of 146 HITs, yielding 3007 responses. A breakdown of responses across conditions is given in Table~\ref{tab:data_collected}.

@@

A \emph{brainstorming run}, or \emph{run}, is the temporally-ordered series of instances that were received in a single HIT by a single worker.

An \emph{idea} is a unique solution to the brainstorming problem. An instance is associated with exactly one \emph{idea}, though multiple instances can be associated with the same idea. Multiple instances of the same idea do not need to be identically phrased to refer to the same idea. For example, in Figure~\ref{fig:example_instances}, we consider ``Storage Container'' and ``Small Storage Box'' as two instances of the same \emph{idea}. However, we do not consider ``Coin Storage'' to be the same idea, since it provides a more specific use case than the previous two.

Despite the differences in specificity between ``Coin Storage'' and the more generic containers, it is useful to encode their relationship. We use hierarchical clusters to encode these relationships. We call a hierarchical cluster of ideas a \emph{category tree}.

@@

\subsubsection{Clustering: Process}
To produce the idea forest, the primary author added instances to the idea forest one at a time using the following method.

@@

Clustering was performed using a custom-built tool that assisted in finding similar instances. Briefly, the tool represented each instance using a bag-of-words model that included synonyms for instance's words. The words were stemmed, then individual instances were ranked according to a cosine similarity metric.

>>>>

\subsection{Recruitment and Remuneration}
We published brainstorming HITs (human intelligence tasks) on Amazon's Mechanical Turk. Workers were residents of the United States to increase the chances of English language comprehension and a shared cultural background.

HITs were placed on the marketplace asking for 5, 10, 20, 50, 75, 100, or as many possible ideas. HITs paid approximately 3.5 cents per idea requested, yielding reward amounts of 18 cents (5), 35 cents (10), 70 cents (20), \$1.75 (50), \$2.65 (75), and \$3.50 (100). For the unlimited condition, we offered \$1.75, pricing it the same as the 50 ideas condition. HITs were advertised with the number of responses requested. Workers had 18 hours to submit the HIT once accepted.

\subsection{Brainstorming Question: Uses for an Old MP3 Player}
In conducting this research, we tested several brainstorming questions, including classic brainstorming questions from prior work (e.g., ``provide alternative uses for a mop''); a request to brainstorm factors that influence weight gain and weight loss; and more goal-oriented questions, such as one requesting people to brainstorm ways to raise funds for a charity. Ultimately, we chose the goal-oriented brainstorming questions since they reflect what we believe would be real-world uses of brainstorming.

The final brainstorming question we chose is the following:
\begin{quote}
{\em Many people have old MP3 players or MP3 players that they no longer use. Please brainstorm N uses for old MP3 players/MP3 players. Assume that the devices' batteries no longer work, though they can be powered via external power sources. Also be aware that devices may {\em not \/} have displays. Be as specific as possible in your descriptions.\/}
\end{quote}

@@

We focus on this problem because a) we expected workers to be familiar with problem area (old MP3 players), b) it represents a real-world problem (what to do with old electronics that are still partially functional), and c) we anticipated there to be a wide range of creative solutions possible. All data presented in this paper refer only to responses received to this particular question.

@@

The introduction listed Osborne's four rules of brainstorming \cite{osborn_applied_1957}, adapted to this context.
%\begin{enumerate}
%\item There are no bad ideas. Don't criticise your choices.
%\item Wild ideas and building off of old ideas are okay.
%\item Quantity of ideas is prioritized.
%\item Combinations of ideas count as new ideas.
%\end{enumerate}
In addition to the visible text input fields, HITs were instrumented to collect the time of the first activation and last de-activation of each form element.

@@

154 workers submitted 170 HITs, for a total of 3292 responses. As we received data in the unlimited condition, it became obvious that this was a poor strategy to employ -- the number of responses received was less than 15 in all cases. We remove that data from our analysis.

If a worker completed multiple HITs, there is the possibility that their responses and idea generation processes evolved over time. Only the first HIT submitted by each worker is retained.

We are left with 146 distinct participants for a total of 146 HITs, yielding 3007 responses. %A breakdown of responses across conditions is given in Table~\ref{tab:data_collected}.

@@

A \emph{brainstorming run}, or \emph{run}, is the temporally-ordered series of instances that were received in a single HIT.

An \emph{idea} is a unique solution to the brainstorming problem. An instance is associated with exactly one \emph{idea}, though multiple instances can be associated with the same idea. For example, in Figure~\ref{fig:example_instances}, we consider ``Storage Container'' and ``Small Storage Box'' as two instances of the same \emph{idea}. However, we do not consider ``Coin Storage'' to be the same idea, since it provides a more specific use case than the previous two. We use hierarchical clusters to encode these relationships. We call a hierarchical cluster of ideas a \emph{category tree}.

@@

\subsubsection{Clustering: Process}
To produce the idea forest, the primary author added instances to the idea forest using the following method.

@@

Clustering was performed using a custom-built tool that assisted in finding similar instances. The tool represented each instance using a query-expanded bag-of-words model ranked according to a cosine similarity metric.

### 2013-10-19 chi2014/related.tex
10 pages

Electronic brainstorming is a variant in which individuals brainstorm at separate computer terminals, with the exchange of ideas performed over the network \cite{gallupe_electronic_1992}. Participants enter ideas while others' ideas are anonymously presented on-screen. As with nominal brainstorming, Gallupe \cite{gallupe_electronic_1992} observed that electronic brainstorming can reduce counterproductive social effects. However, Pinsonneault et al.\ \cite{pinsonneault_electronic_1999} identify productivity impediments introduced by group electronic brainstorming, such as being distracted by other ideas appearing, and individuals witholding ideas they feel are derivative of others. They find little evidence to support the proposition that electronic brainstorming outperforms nominal brainstorming.

@@

Shifting our focus to an \emph{individual's} brainstorming processes, Nijstad and Stroebe provide a model for individual idea generation dubbed SIAM, or the ``search for ideas in associative memory'' \cite{nijstad_how_2006}. SIAM defines two stages of idea generation: the generation of ideas based on working memory, and idea production within a single activated ``image'' (where an image can be thought of as a category of ideas). This model makes predictions, one of the most important being that an idea is more likely to be followed by an idea in the same category than would be expected by chance. Their model also predicts that new ideas in the same category as the previous idea are generated faster than ideas between categories. Nijstad and Stroebe verified these predictions in the context of nominal brainstorming.

To assess the brainstorming process and its outputs, a number of measures have been proposed. Typically, the measures of concern are the novelty of generated ideas, the practicality/appropriateness of ideas, the variety of ideas (flexibility), and the quantity of ideas generated. \cite{finke1992creative, shah2003metrics}.

The most common approach to measure novelty and appropriateness is to ask domain experts to subjectively make scale-rated assessment of each \cite{lewis2011affective, amabile_1983}. These two measures are sometimes combined into one measure of quality \cite{little2010exploring}.
Some researchers opt for a measure that can be derived objectively. For example, Jansson et al. used `o' scores, derived from the frequency with which an idea occurs, to evaluate novelty \cite{jansson_design_1991}. We adopt this use of o-score in our later analyses.

@@

\subsection{Crowdsourced Brainstorming}
%The simplest imaginable instantiation of brainstorming in a microtask marketplace mirrors that of nominal brainstorming. More sophisticated environments are possible, such as those that forward ideas that others have generated (electronic brainstorming). 
%Examples for these environments are platforms for generating social innovation ideas or product concepts like OpenIDEO, Quirky and Threadless that employ structured process where participants take on different responsibility from generating ideas to evaluating others' ideas.
We constrain our focus to nominal brainstorming in this environment with the goal of establishing baselines.

>>>>

Electronic brainstorming is a variant in which individuals brainstorm at separate computer terminals, with the exchange of ideas performed over the network \cite{gallupe_electronic_1992}. As with nominal brainstorming, Gallupe \cite{gallupe_electronic_1992} observed that electronic brainstorming can reduce counterproductive social effects. However, Pinsonneault et al.\ \cite{pinsonneault_electronic_1999} identify productivity impediments introduced by group electronic brainstorming, such as being distracted by other ideas appearing, and individuals witholding ideas they feel are derivative. They find little evidence to support the proposition that electronic brainstorming outperforms nominal brainstorming.

@@

Shifting our focus to an \emph{individual's} brainstorming processes, Nijstad and Stroebe provide a model for individual idea generation dubbed SIAM, or the ``search for ideas in associative memory'' \cite{nijstad_how_2006}. SIAM defines two stages of idea generation: the generation of ideas based on working memory, and idea production within a single activated ``image'' (where an image can be thought of as a category of ideas). This model predicts that an idea is more likely to be followed by an idea in the same category than would be expected by chance. SIAM also predicts that new ideas in the same category as the previous idea are generated faster than ideas between categories. Nijstad and Stroebe verified these predictions in the context of nominal brainstorming.

To evaluate brainstorming, a number of measures have been proposed: novelty , practicality/appropriateness, variety, and quantity. \cite{finke1992creative, shah2003metrics}.
The most common approach to measure novelty and appropriateness is to ask domain experts to make scale-rated assessment of each \cite{lewis2011affective, amabile_1983}. These two measures are sometimes combined into one measure of quality \cite{little2010exploring}.
Some researchers opt for a measure that can be derived objectively. For example, Jansson et al. used `o' scores, derived from the frequency with which an idea occurs, to evaluate novelty \cite{jansson_design_1991}. We adopt this use of o-score in our later analyses.

@@

\subsection{Crowdsourced Brainstorming}
%The simplest imaginable instantiation of brainstorming in a microtask marketplace mirrors that of nominal brainstorming. More sophisticated environments are possible, such as those that forward ideas that others have generated (electronic brainstorming). 
%Examples for these environments are platforms for generating social innovation ideas or product concepts like OpenIDEO, Quirky and Threadless that employ structured process where participants take on different responsibility from generating ideas to evaluating others' ideas.
%We constrain our focus to nominal brainstorming in this environment with the goal of establishing baselines.

### 2013-10-19 chi2014/results.tex
10 pages

We use an identical model for modeling the rate at which new idea categories are introduced over time. Figure~\ref{fig:cumulative_categories} shows the data and fitted model for the cumulative number of novel categories over time. For this model, we obtain a $y_{scale}$ value of 2.1 (HDI 2.0-2.2), with a $rate$ of 0.67 (HDI 0.66-0.67). Again, we find very clear support that the rate of novel categories is non-linear as a function of the number of responses received.

@@

In both cases, we observe a steady increase in o-scores for the first 20-30 responses. After these first 20-30 responses, the o-scores plateau, with no clear discernible pattern for either ideas or idea categories.

This lends support for hypothesis 2, the notion that there is a set of general, common ideas that make up the first several responses of every crowd brainstorming session, regardless of condition.

@@

\subsection{Idea Generation Patterns}
Given the differences in originality and rarity as a function of response number, we now consider idea generation patterns observable from the data. We examine these patterns in the context of hypotheses 4 and 5, which draw upon the SIAM model of brainstorming. This model predicts individuals will generate ideas within ``images'' or categories of ideas (i.e., ``riff'' on an idea or concept) before switching to a new category.

We can identify riffing by examining whether a response instance belongs to the same category tree as the previous instance. We can then derive a number of statistics from these data. Below is an excerpt of a particular participant's brainstorming run.

@@

Table~\ref{tab:riffing} provides a summary of riffing statistics observed in our data set. We find that the higher the number of instances requested, the more likely participants are to use old ideas as inspiration for new ideas. However, we observe that riff sequences are typically quite small in length, across conditions.

@@

SIAM predict that individuals will generate ideas from an idea category until they exhaust that category, at which point they switch to another category (hypothesis 3). Furthermore, SIAM predicts that this category switching will be observable as taking more time to generate an idea in a new category than in the existing category (hypothesis 4). We examine each of these hypotheses in turn.

@@

To determine category switching, we examine whether an idea is assigned to the same category tree as the previous instance, or whether it was assigned to a different category tree.

@@

To calculate the time to generate a response instance, we examine the times logged for the first and last activation of a text entry widget.

An examination of the timing data suggests a log-normal distribution. We fit two models: $t_w = \text{lognormal}(\mu_w, \sigma_w)$ for within-category idea generation and $t_b = \text{lognormal}(\mu_b, \sigma_b)$ for between-category idea generation, where the $t$ parameter in each model represents the time spent generating an instance.

@@

The resulting models fitted to the data are shown in Figure~\ref{fig:hyp5_comparison}. The mean for the within-category condition was 9.5 in log space (13.4 seconds, HDI 9.4-9.6), while the mean for the between-categories condition was 10.2 (27.0 seconds, HDI 10.2-10.3). The differences in mean are significant and confirm hypothesis 4. Notably, within-category instance generation took an average of 12.6 seconds less than between-categories instance generation, consistent with the findings of Nijstad and Stroebe, who reported differences of 6-12 seconds.

>>>>

We use an identical model for the rate at which new idea categories are introduced over time. Figure~\ref{fig:cumulative_categories} shows the data and fitted model for the cumulative number of novel categories over time. For this model, we obtain a $y_{scale}$ value of 2.1 (HDI 2.0-2.2), with a $rate$ of 0.67 (HDI 0.66-0.67). Again, we find very clear support that the rate of novel categories is non-linear as a function of the number of responses received.

@@

In both cases, we observe a steady increase in o-scores for the first 20-30 responses, followed by a plateau.
This lends support for hypothesis 2, the notion that there is a set of general, common ideas that make up the first several responses of every crowd brainstorming session, regardless of condition.

@@

\subsection{Idea Generation Patterns}
Given the differences in originality and rarity as a function of response number, we now consider idea generation patterns in the context of hypotheses 4 and 5. The SIAM model of brainstorming predicts individuals will generate ideas within ``images'' or categories of ideas (i.e., ``riff'' on an idea or concept) before switching to a new category.

We identify riffing by examining whether a response instance belongs to the same category tree as the previous instance. We can then derive a number of statistics from these data. Below is an excerpt of a brainstorming run (PXXX):

@@

Table~\ref{tab:riffing} provides a summary of riffing statistics observed in our data set. The higher the number of instances requested, the more likely participants are to use old ideas as inspiration. Riff sequences are typically quite small in length.

@@

SIAM predict that individuals will generate ideas from an idea category until they exhaust that category, at which point they switch to another category (hypothesis 3). Furthermore, SIAM predicts that this category switching will be observable as taking more time to generate an idea in a new category than in the existing category (hypothesis 4). %We examine each of these hypotheses in turn.

@@

To determine category switching, we examine whether an idea is assigned to the same category tree as the previous instance.%, or whether it was assigned to a different category tree.

@@

To calculate the time to generate a response instance, we take the difference between the first and last activation of a text entry widget.
We fit two models: $t_w = \text{lognormal}(\mu_w, \sigma_w)$ for within-category idea generation and $t_b = \text{lognormal}(\mu_b, \sigma_b)$ for between-category idea generation, where the $t$ parameter in each model represents the time spent generating an instance.

@@

The resulting models fitted to the data are shown in Figure~\ref{fig:hyp5_comparison}. The mean for the within-category condition was 9.5 in log space (13.4 seconds, HDI 9.4-9.6), while the mean for the between-categories condition was 10.2 (27.0 seconds, HDI 10.2-10.3). The differences in mean are significant. Notably, within-category instance generation took an average of 12.6 seconds less than between-categories instance generation, consistent with the findings of Nijstad and Stroebe, who reported differences of 6-12 seconds.
